Pool Model - A unified Mathematical\\ Modeling Framework for Food Science

### 2025-11-07 paper/pool_model.tex
add citation to book our chapter
add Christian's e-mail
Use pdf images for spatial curves

\cortext[cor1]{Corresponding Author}
\fntext[fn1]{jonas.pleyer.org}
\affiliation[1]{
    organization={Freiburg Center for Data Analysis and Modeling},
    addressline={Ernst-Zermelo Str. 1},
    city={Freiburg im Breisgau},
    postcode={79104},
    country={Germany},
}

@@

bacterial growth dynamics~\citep{perez-rodriguez_predictive_2012}.

@@

        {Figures-abm-homogenous-abm_ode_comparison.png}

@@

        {Figures-abm-homogenous-low-diffusion-abm_ode_comparison.png}

@@

        {Figures-abm-inhomogenous-abm_ode_comparison.png}

@@

        {Figures-abm-random-abm_ode_comparison.png}

>>>>

\fntext[fn1]{jonas.pleyer.org}
\cortext[cor1]{Corresponding Author\\ \textit{E-mail address:} christian.fleck@fdm.uni-freiburg.de}
\affiliation[1]{
    organization={Freiburg Center for Data Analysis and Modeling},
    addressline={Ernst-Zermelo Str. 1},
    city={Freiburg im Breisgau},
    postcode={79104},
    country={Germany},
}

@@

bacterial growth dynamics~\citep{perez-rodriguez_predictive_2012, gaindrik_experimental_2025}.

@@

        {Figures-abm-homogenous-abm_ode_comparison.pdf}

@@

        {Figures-abm-homogenous-low-diffusion-abm_ode_comparison.pdf}

@@

        {Figures-abm-inhomogenous-abm_ode_comparison.pdf}

@@

        {Figures-abm-random-abm_ode_comparison.pdf}
